Methods and Results

### 2021-04-30 ms.Rmd
Fixing code for one function. Adding stats methods. Need one more section fro results, few more paragrahs on methods

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: false
      reference_docx: template.docx
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, ggarrange)
  source("./R/func.R")
```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)

@@

@@

  model1.1 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
    robust <- robust(model1.1, cluster = data$study)

@@

  AIC(model1.2, model1.1) # Phylogeny explains very little variation; model without phylogeny better supported, even if slightly. Just keep species in model

# Table 1: Effect, confidemce intervals, prediction intervals, heterogenity
            table1 <- make_table(model1.1, data)
      hetero_table <- I2(model1.1, v = data$v_SMDH) # Same as orchaRd::i2_ml(model1.1)
hetero_table_phylo <- I2(model1.2, v = data$v_SMDH, phylo = "species2")

@@

@@

Overall, we collected effect sizes for a total of `r length(unique(data$species))` species from `r length(unique(data$study))` studies. Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%). We obtained `r table(data$Harm_type)[2]` effect sizes from manipulations on species that resulted in direct harm (e.g., traumatic insemination), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females (e.g., mating rate and harassment). A total of `r table(data$Harm_type)[1]` effect sizes were from experiment where females received both direct and indirect harm from male matings.

Across all species, we obtained `r table(data$Gestation)[1]` effects from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` effects from `r parity[2,2]` viviparous species. Unfortunately, effect sizes from viviparous species were all take from studies on fish species with indirect male harm. As such, we analyzed only 'harm type' and an index of sexual size dimorphism.

@@

Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`). This strong effect held even when accounting for within-study non-independence (Meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`). However, visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)). Evidence for publication bias was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`), and this held true when accounting for heterogenity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`). Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguisable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`). It is important recognise that the corrected meta-analytic mean is simply a sensitivity analysis, and we cannot know for certain whether there indeed are and how many, missing studies.

When accouting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects. The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).

@@

autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
ft <- flextable(table1)
ft <- set_caption(ft,  caption = "Effect size", autonum = autonum)
ft <- set_header_labels(ft, n = md("$n_{effects}$"),
                    std = md("**n<sub>studies<sub>**"),
                     spp = md("**n<sub>species<sub>**"),
                  est = md("**Meta-analytic mean**"),
                    CI = md("**95% CI**"),
                    PI = md("**95% PI**"),
              i2_stdy = md("***I*<sup>2</sup><sub>study</sub>\n(%)**"),
            i2_trait = md("***I*<sup>2</sup><sub>trait</sub>\n(%)**"),
           i2_species = md("***I*<sup>2</sup><sub>species</sub>\n(%)**"),
             i2_tot = md("***I*<sup>2</sup><sub>total</sub>    \n(%)**"))
ft

@@

@@

```{r SSD, fig.width=6, fig.height=4.5}
p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH))) + 
    geom_point() + 
      theme_bw() + 
  labs(x = "SSD", 
	     y = "SMDH",
	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
	guides(size = guide_legend(direction = "vertical"))

@@

>>>>

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: false
      reference_docx: template.docx
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn)
eval(metafor:::.MuMIn)
source("./R/func.R")

```
```{r loaddata, echo = FALSE, results = "hide"}
################
# Tree
################
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)

@@

  # Number of effects per study
  n_eff_study <- data %>%
                  group_by(study) %>%
                  summarise(n = n())
  n_eff_study <- range(n_eff_study$n)

@@

  model1.1 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, 
                     random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
    robust <- robust(model1.1, cluster = data$study, vcov = "CR2")

@@

   aics <- AICc(model1.2, model1.1) # Phylogeny explains very little variation; model without phylogeny better supported, even if slightly. Just keep species in model
  dAICc <- max(aics$AICc) - min(aics$AICc)

# Table 1: Effect, confidemce intervals, prediction intervals, heterogenity
   hetero_table <- metaAidR::I2(model1.1, v = data$v_SMDH, obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
   hetero_table_phylo <- metaAidR::I2(model1.2, v = data$v_SMDH, phylo = "species2", obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
         table1 <- make_table(model1.1, heteroTable = hetero_table)

@@

#### Meta-analysis
We analysed effect size data using the *metafor* (@Metafor - vers 2.4.0) package in R (@R - vers 4.0.5). To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) (@nakagawa2012methodological). Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study. To control for sources of non-independence, we included study and species-level random effects (@Noble2017). We also fit a model that included a species-level  random effect with a phylogenetic correlation matrix. However, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`). As such, we did not include phylogeny in our models. Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes derived from common treatment groups or effect sizes derived from different traits measured on the same individuals (@Noble2017). We therefore applied robust variance estimators (RVEs) to correct standard errors from our models. RVEs have been shown to be robust estimators of standard errors from meta-analytic models when effect sizes within studies are not indpendent. In addition, one does not need to assume or specify how such effects are correlated  (@Song2021), making them easier to apply.

Using our MLMA models we estimated effect size heterogenity as $I^2$ (@nakagawa2012methodological). $I^2_{study}$ and $I^2_{species}$ were the proportion of effect size variance over total variance as a result of between study and species effects, respectively. $I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.

@@

Overall, we collected effect sizes for a total of `r length(unique(data$species))` species from `r length(unique(data$study))` studies. Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%). We obtained `r table(data$Harm_type)[2]` effect sizes from manipulations on species that resulted in direct harm (e.g., traumatic insemination), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females (e.g., mating rate and harassment). A total of `r table(data$Harm_type)[1]` effect sizes were from experiments where females received both direct and indirect harm from male matings.

Across all species, we obtained `r table(data$Gestation)[1]` effects from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` effects from `r parity[2,2]` viviparous species. Unfortunately, effect sizes from viviparous species were all taken from studies on fish species with indirect male harm. As such, we analyzed only 'harm type' and an index of sexual size dimorphism.

@@

Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`). This strong effect held even when accounting for within-study non-independence (Meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`). However, visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)). Evidence for publication bias was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`), and this held true when accounting for heterogenity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`). Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguisable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`). It is important recognise that the corrected meta-analytic mean is simply a sensitivity analysis. We cannot know for certain whether publication bias treuly exists, and if so, how many missing studies exist.

When accounting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects. The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).

@@

autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
ft <- flextable(table1)
ft <- set_caption(ft,  caption = "Effect size", autonum = autonum)
ft <- set_header_labels(ft, n = TeX("$n_{effects}$"),
                          std = md("**n<sub>studies<sub>**"),
                          spp = md("**n<sub>species<sub>**"),
                          est = md("**Meta-analytic mean**"),
                           CI = md("**95% CI**"),
                           PI = md("**95% PI**"),
                      i2_stdy = md("***I*<sup>2</sup><sub>study</sub>\n(%)**"),
                     i2_trait = md("***I*<sup>2</sup><sub>trait</sub>\n(%)**"),
                   i2_species = md("***I*<sup>2</sup><sub>species</sub>\n(%)**"),
                       i2_tot = md("***I*<sup>2</sup><sub>total</sub>    \n(%)**"))
ft

@@

Male harm type impacted the overall magnitude of effects.

@@

```{r SSD, fig.width=6, fig.height=4.5}
p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH))) + 
    geom_point() + 
      theme_bw() + 
  labs(x = "Sexual Size Dimorphism (SSD) Index", 
	     y = "SMDH",
	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
	guides(size = guide_legend(direction = "vertical"))

@@

# References
